---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(farsfunctions)
```

# Coursera Assignment for Building an R Package

My build is passing on AppVeyor and Travis!

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/VirenDias/farsfunctions?branch=master&svg=true)](https://ci.appveyor.com/project/VirenDias/farsfunctions)

[![Travis-CI Build Status](https://travis-ci.org/VirenDias/farsfunctions.svg?branch=master)](https://travis-ci.org/VirenDias/farsfunctions)

## Installation

You can install farsfunctions from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("VirenDias/farsfunctions")
```

## Reading a CSV File

To read a CSV file and return a data frame table of the data, you should use the *fars_read* function. To make things easier, use it in conjunction with the *make_filename* function and specify the year of data you would like to read.

```{r}
fars_read(make_filename(2015))
```

## Reading Accident Data Across Multiple Years

To read accident data across multiple years, you should use the *fars_read_years* function and specify the years of data you would like to read.

```{r}
fars_read_years(c(2013, 2014, 2015))
```

## Summarizing Accident Data Across Multiple Years

To summarize accident data across multiple years, you should use the *fars_summarize_years* function and specify the years of data you would like to summarize.

```{r}
fars_summarize_years(c(2013, 2014, 2015))
```

## Plotting Accident Data

To plot accident data on a geographical map, you should use the *fars_map_state function*, and specify the state number and year of accident data to plot.

```{r}
fars_map_state(1, 2015)
```
