---
title: "How to Use FARS Functions"
author: "Viren Dias"
date: "2018-03-14"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(farsfunctions)
```

This document will explain how to use the FARS functions to analyse accident data.

## Reading a CSV File

To read a CSV file and return a data frame table of the data, you should use the *fars_read* function. To make things easier, use it in conjunction with the *make_filename* function and specify the year of data you would like to read.

```{r}
fars_read(make_filename(2015))
```

## Reading Accident Data Across Multiple Years

To read accident data across multiple years, you should use the *fars_read_years* function and specify the years of data you would like to read.

```{r}
fars_read_years(c(2013, 2014, 2015))
```

## Summarizing Accident Data Across Multiple Years

To summarize accident data across multiple years, you should use the *fars_summarize_years* function and specify the years of data you would like to summarize.

```{r}
fars_summarize_years(c(2013, 2014, 2015))
```

## Plotting Accident Data

To plot accident data on a geographical map, you should use the *fars_map_state function*, and specify the state number and year of accident data to plot.

```{r}
fars_map_state(1, 2015)
```
